Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-03 documentation/paper.tex
Introduced MLP for FFT analysis

A convolutional neural network was used for analyzing the raw waveform directly, without any preprocessing whatsoever. This avoids any destruction of information, and should be possible, in theory, for a neural network to handle. For this task, a very deep 1-dimensional fully convolutional neural network was applied. The architecture was inspired by the M34-res network \cite{verydeepconvnets} for analysis of raw waveforms. (Its hyperparameters were modified significantly through manual empirical testing as well as grid searches.)

Two different configurations were tested: one that operates strictly on the waveform with no position corrections of any kind (furthermore $DeepConv(\omega)$) and one with an additional position input on a lower layer such that it should be able to learn to incorporate position corrections into its outputs ($DeepConvWithPos(\omega, \chi)$). The second configuration was introduced because the position corrections applied to $\beta_{8}$ in previous PICO-60 research were applied only to broad frequency bands and are thus not practical to apply to a full resolution waveform.

@@

>>>>

A convolutional neural network was used for analyzing the raw waveform $\omega$ directly, without any preprocessing whatsoever. This avoids any destruction of information, and should be possible, in theory, for a neural network to handle. For this task, a very deep 1-dimensional fully convolutional neural network was applied. The architecture was inspired by the M34-res network \cite{verydeepconvnets} for analysis of raw waveforms. (Its hyperparameters were modified significantly through manual empirical testing as well as grid searches.)

Two different configurations were tested: one that operates strictly on $\omega$ with no position corrections of any kind (furthermore $DeepConv(\omega)$) and one with an additional position input on a lower layer such that it should be able to learn to incorporate position corrections into its outputs ($DeepConvWithPos(\omega, \chi)$). The second configuration was introduced because the position corrections applied to $\beta_{8}$ in previous PICO-60 research were applied only to broad frequency bands and are thus not practical to apply to a full resolution waveform.

@@

\subsection{Multi-Layer Perceptron for Fourier Transform Analysis}

A multi-layer perceptron (a neural network composed of fully connected layers) was applied to analysis of audio data in the frequency domain. Preprocessing by applying a Fourier transform makes it an easier task for the neural network to accomplish in some ways. If the frequency distribution and overall volume are indeed the most important factors for discrimination, the network can gather them straight from the Fourier transform $\beta_{N}$ rather than having to analyze $\omega$ to extract this information.
